---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(tidyverse)
```
# turnR

<!-- badges: start -->
<!-- badges: end -->

The turnR package contains several functions that I find useful.  Feel free to use them and recomended changes and updates as you desire.  Thanks!

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dusty-turner/turnR")
```
## Example `theme_turnR`

This is an example which shows you how to use the `theme_turnR` function for ggplot2.

```{r example theme_turnR}
library(turnR)
data("diamonds")
diamonds %>%
  ggplot(aes(x=carat,y=price,color=cut,fill=cut)) +
  geom_point() +
  labs(title = "Diamonds Data") +
  theme_turnR()
```

## Example 2 `theme_turnR_f`

This is an example which shows you how to use the `theme_turnR_f` function for ggplot2.

```{r example theme_turnR_f}
library(turnR)
data("diamonds")
diamonds %>%
  ggplot(aes(x=cut,y=price,color=cut,fill=cut)) +
  geom_violin() +
  labs(title = "Diamonds Data") +
  facet_wrap(~clarity) +
  theme_turnR_f()
```

## Example 3 `randtest` and `randtestvis`

```{r}
set.seed(256)
x=rnorm(100,1,0)
y=rnorm(100,1.1,1)
rt = randtest(x,y,fun = mean, reps = 10000)
rt[2] 
rt[3] 
randtestviz(x,y,fun = mean, reps = 10000)
```

## Cats

Oh, and everyone likes cats

```{r}
mycat(CatName = "BeatNavy")
```

